
\section{Current Focus}

\outerlist{

\entrybig{\textbf{Understanding Fundamental Cognitive Capabilities of AI}}{Harvard University}{Collaborators: Dr. Hidenori Tanaka, Dr. Ekdeep Singh Lubana}{Feb 2024\textendash Current}{}
\innerlist{
    \entry{\textbf{Understanding phase changes of in-context learning}: Understanding how AI models transition between different mechanisms for in-context learning depending on the data distribution and design choices.}
    \entry{\textbf{Understanding inference scaling}: Understanding how in-context exemplars shape large language model's representation and mechanisms.}
    \entry{\textbf{Understanding hidden emergence of capabilities}: Understanding hidden emergence of capabilities in text-to-image generative models: showed a hidden phase transition of a compositional capability.}
 }
 
\entrybig{\textbf{Compositional Generalization in Spectral Space}}{Harvard University}{Advisor: Dr. Cecilia Garraffo, Dr. Douglas Finkbeiner}{Sep 2023\textendash Current}{}
\innerlist{
	\entry{\textbf{MethaneSAT}: Developed a spectral classification and correction algorithm, \textit{iterative logistic regression}, to classify cloud covered regions and correct for the effect of shadows on the observed spectra
	}
     \entry{\textbf{TEMPO}: Currently developping a convolutional variational auto-encoder to jointly compress and segment hyperspectral data from TEMPO. The goal is to enhance prediction of NO densities, which is a major public health concern.}
    }
}
