
\section{Past Projects}
\outerlist{

\entrybig{\textbf{Deep Learning and Computer Vision for Neuroscience}}{Harvard University}{Advisor: Dr. Aravinthan Samuel, Dr. Jeff Lichtman}{Aug 2020\textendash Sep 2024}{}
\innerlist{
        \entry{\textbf{Few-shot 3D volumetric tracking, developed \href{https://www.nature.com/articles/s41592-023-02096-3}{targettrack}.}}
	\entry{\textbf{Machine learning driven accelerated connectomics, co-developed \href{https://www.biorxiv.org/content/10.1101/2023.10.05.561103v2}{SmartEM}.}}
 	\entry{\textbf{Image compression using deep learning, co-developed \href{https://www.biorxiv.org/content/10.1101/2024.07.07.601368v1}{EM-Compressor}.}}
}

\entrybig{\textbf{Emulating the structure of the universe using diffusion models}}{Harvard University}{With: Dr. Carolina Cuesta-Lazaro}{Aug 2023\textendash Aug 2024}{}
\innerlist{
	\entry{\textbf{Probabilistic emulation, debiasing and completion of the large scale structure of matter distribution using diffusion models.}}
}

\entrybig{\textbf{Whole Brain Imaging}}{Harvard University}{Advisor: Dr. Aravinthan Samuel}{Apr 2021\textendash May 2023}{}
\innerlist{
	\entry{\textbf{Identifying neural circuits for C.elegans thermotaxis via automated whole brain imaging.}}
}

\entrybig
	{\textbf{Astro-statistics}}{Harvard University}
	{Advisor: Dr. Douglas Finkbeiner}{Sep 2020\textendash Oct 2022}
\innerlist{
        \entry{\textbf{Fourier space sparse wavelet transform on the GPU}}
	\entry{\textbf{Quantifying the non--Gaussianity of high--dimensional statistics}}
        \entry{\textbf{Estimating correlations of large scale structure and galactic dustmaps}}
}

\entrybig
	{\textbf{Experimental Particle Physics}}{KAIST}
	{Advisor: Dr. Jonghee Yoo}{Dec 2018\textendash Feb 2019}
\innerlist{
	\entry{\textbf{Real-time DAQ system for the CAPP18T Axion Dark Matter Experiment}}
}

}